### 2014-03-08 src/analysis.Rnw
update

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\label{fig:xsamplesel}
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again.

The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}

% ----------------------------------------------------------------------
<<count>>=
stats.loc <- subset(stats.rest, grepl('^(l|wl)[.]', operator))

o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(l|wl)[.]', operator))
colnames(o.stats.sel.loc) <- new.colnames
colnames(r.stats.sel.loc) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.loc, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.loc, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\bigskip
\caption {The loc count selection criteria results.}
\end{table*}

>>>>

\begin{figure*}[t]
<<x.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.xp <- subset(o.processed, grepl('^rr[.].*.m[.]red',ind))
ggplot(subset(o.xp, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\caption{The effect of sample(x) reduction. All are above 0.90 $R^2$.}
\label{fig:xsamplesel}
\end{figure*}
%TODO : See if the following paragraph is needed, or shall we just sink the ceil(x) discussion completely?
Our experiments found that while $round(x)$ and $sample(x)$ produced relatively reasonable reduction of mutants, the $ceil(x)$ criteria failed to produce a reasonable reduction of mutants except for higher power where the reduction was some what close to that produced by $round(x)$ and $sample(x)$ (which was expected). The $R^2$ values of $ceil(x)$ were almost always lower than that produced by $round(x)$ and $sample(x)$ for similar reduction of mutants. For this reason, we do not consider this function again. However, interested parties can refer to our published data.

The reduction in mutants for x\% selection using $round(x)$ is graphed in Figure~\ref{fig:xroundsel}. The values for the same are given in Table~\ref{tbl:xsel}.
Similarly reduction in mutants for x\% selection using $sample(x)$ is graphed in Figure~\ref{fig:xsamplesel}. The values for the same are given in Table~\ref{tbl:xsel}.
% ----------------------------------------------------------------------

\subsubsection{Lines per element}
The aim of this criteria is similar in some sense to selective mutation. While n-selective mutation ignores the most numerous mutant species, this criteria seeks to deprioritize the most complex program elements.

<<count>>=
stats.loc <- subset(stats.rest, grepl('^(l|wl)[.]', operator))
o.stats.sel.loc <- subset(o.f(stats.loc), select=sel.colnames)
r.stats.sel.loc <- subset(r.f(stats.loc), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(l|wl)[.]', operator))
colnames(o.stats.sel.loc) <- new.colnames
colnames(r.stats.sel.loc) <- new.colnames
@
\begin{table*}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(o.stats.sel.loc, caption='Original', label='table:rando'), include.rownames=FALSE, floating=FALSE, size='\\small')
@
\end{minipage}
\hspace{0.5cm}
\begin{minipage}[h]{0.49\linewidth}
<<results='asis'>>=
print(xtable(r.stats.sel.loc, caption='Randoop', label='table:randr'), include.rownames=FALSE, floating=FALSE,size='\\small')
@
\end{minipage}
\caption {The line count selection criteria results.}
\label{tbl:locsel}
\end{table*}

\begin{figure*}[t]
<<loc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc <- subset(o.processed, grepl('^l[.].*.m[.]red',ind))
ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\caption{The effect of loc (external) reduction. All are above 0.98 $R^2$.}
\label{fig:locsel}
\end{figure*}

\begin{figure*}[t]
<<wloc.per.sel.sample,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='8in', echo=F, message=F, warn=F,fig.lp="fig:">>=
o.loc <- subset(o.processed, grepl('^wl[.].*.m[.]red',ind))
ggplot(subset(o.loc, values < 100), aes(power, values, fill=interaction(type,power), dodge=type)) +
  stat_boxplot(geom ='errorbar')+
  geom_boxplot() + facet_wrap(~type)
@
\caption{The effect of loc (internal) reduction. All are above 0.90 $R^2$.}
\label{fig:wlocsel}
\end{figure*}

The results of this selection criteria are provided in Table~\ref{tbl:locsel}. The effect of random selection within the program elements are visualized in Figure~\ref{fig:wlocsel}, and when it is made external to the program elements is visualized in Figure~\ref{fig:wlocsel}.
